Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-01 paper/main.tex

>>>>

\begin{tabular}{|c|c|}
\hline 
HSLDA & sLDA with Independent Regressors\tabularnewline
\hline 
children, animation, animated, kids, songs, story, & children, kids, animated, 
\tabularnewline
family, new, fun,video, friends, music, live, classic, & animation, songs, video, friends, fun, animals, family, story, 
\tabularnewline
adventure, minute, world, magic,animals, song, musical, & new, little, music, like, minute, along, musical, song,
\tabularnewline
voiced, feature, along, baby, ages, magical, & adventure, help, classic, baby, child, ages, favorite, sing, learn,
\tabularnewline
action, favorite, special, tale, little, child, holiday, & holiday, magical, tale, world, special, parents, live, way, day, boy,
\tabularnewline
help, voice, toys, original, learn, characters, & make, old, magic, adventures, home, show, gang, animal, adults, toys,
\tabularnewline
computer, sing, like, adults, parents, version, old, first, & many, action
\tabularnewline
including, young, 
\tabularnewline
\hline
comedy, funny, comic, hilarious, series, gags, jokes, slapstick, satire, & comedy, show, play, characters, sketches,
\tabularnewline
laugh, stars, films, comedies, first, comedian, funniest, show, involving, & funny, mob, performance,
\tabularnewline
characters, cast, perfect, mob, performance, play, writer, television, & people, screwball, cast, best, including, stars, sketch, girlfriend,
\tabularnewline
satirical, lines, hilariously, boss, routine, silent, funnier, comedic, & hilariously, charming, ensemble, comic, character, star, writer, hit,
\tabularnewline
chemistry, comedians, talk, routines, brothers, girlfriend, shorts, & stage, host, classic, romantic, mutants, boss, new, played, together,
\tabularnewline
mouse, whose, cinema, screwball, hit, humor, brilliant, gag, new,  & choice, like, karaoke, daughter, vehicle, news, splitting, actress,
\tabularnewline
& get, story, hilarious, wacky, featuring, could, side, comedies, comedic\tabularnewline
\hline 
thriller, horror, murder, crime, killer, police, mystery, detective, & horror, film, vampire, blood, one, dead, supernatural, killer, evil,
\tabularnewline
cop, one, dead, suspense, plot, case, blood, drug, dark, mysterious, & thriller, gore, monster, young, night, terror, mysterious, director,
\tabularnewline
death, revenge, violence, town, gang, turns, prison, noir, violent, & movie, films, cult, creepy, terrifying, original, dark, chilling,
\tabularnewline
deadly, stars, young, woman, nbsp, body, vampire, night, murders, & genre, atmosphere, victims, classic, murder, haunted, town, mystery,
\tabularnewline
kill, criminal, action, becomes, wife, cops, gangster, sex, victims, & story, body, ghost, tale, family, murders, castle, house, nightmare,
\tabularnewline
victim, brutal, terror, evil, murdered & budget, eerie, death, doctor, victim, later, bloody, effects
\tabularnewline
\hline 
workout, body, yoga, video, moves, dance, minute, program, fitness, & workout, body, yoga, video, moves, dance, minute,
\tabularnewline
easy, poses, muscles, routine, exercises, learn, strength, movements, & program, fitness
\tabularnewline
practice, help, step, w, workouts, minutes, techniques, flexibility, & easy, poses, muscles, exercises, learn, routine, strength, movements,
\tabularnewline
get, exercise, one, instructor, first, series, time, instruction, & minutes, get, help, practice, step, series, techniques, workouts,
\tabularnewline
use, follow, training, breathing, two, basic, back, ll, muscle, fun, & time, flexibility, exercise, instructor, instruction, one, two, fun,
\tabularnewline
warm, steps, technique, balance, beginners, designed, using & training, use, first, back, follow, steps, breathing, muscle, basic,
\tabularnewline
& using, ll, beginners, three, warm, balance, technique, designed\tabularnewline
\hline
\end{tabular}

### 2011-06-01 paper/related_work.tex

While there has been much work in multi-label classification of text and
text modeling in general, we focus here on topic modeling approaches.
% Noemie: do we need that much text on LDA?
Latent Dirichlet allocation (LDA) is a generative probabilistic model which
represents documents as a mixed-membership bag of word. Each document is
represented as a collection of words, generated from a set of topic assignments
(one for each word), where each topic assignment is drawn from a distribution
over topics~\citep{Blei2003}. sLDA is latent Dirichlet allocation (LDA)
\cite{Blei2003} augmented with per-document labeling, often taking the form of
a single numerical or categorical label. Examples of labels include rating
associated with an online  eview, grades for an essay, and number of times a
webpage is linked. This approach has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression~\cite{BleiMcAuliffe2008}.

% Noemie: check out what I wrote here, because I am not really sure this is
% correct. 
There have been several models that incorporate both latent models of text and
some form of
supervision~\citep{Ramage2009,DiscLDA,wangbleifeifei08,RelationalLDA}. One set 
of models that are particularly relevant to HSLDA are Chang and Blei's
hierarchical models for document networks (Relational Topic Models). In that
family of models, they encountered a similar scenario where an unselected label 
does not always indicate absence. In hierarchical labels, this phenomenon is
even more pervasive -- there are no explicit negative labels, but it is also
unclear how to treat the parents of selected labels. Like in the work of Chang
and Blei, we employ regularization to account for the lack of negative
labeling. In our experiments, we look at the impact of assigning positive and
negative instances to the ancestors of selected labels.

>>>>

While there has been much work in multi-label classification of text and
text modeling in general, we focus here on topic modeling approaches.
Latent Dirichlet allocation (LDA) is a generative probabilistic model which
represents documents as a mixed-membership bag of word. Each document is
represented as a collection of words, generated from a set of topic assignments
(one for each word), where each topic assignment is drawn from a distribution
over topics~\citep{Blei2003}. sLDA is latent Dirichlet allocation (LDA)
\cite{Blei2003} augmented with per-document labeling, often taking the form of
a single numerical or categorical label. Examples of labels include rating
associated with an online  eview, grades for an essay, and number of times a
webpage is linked. This approach has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression~\cite{BleiMcAuliffe2008}.

%Latent dirichlet allocation (LDA) is a generative
%probabilistic model of corpora that represents documents as a mixed
%membership bag-of-words. Also known as topic models, these models
%infer the latent structure, or topics, of documents in a corpus. Each
%document is represented as a collection of words, generated from a
%set of topic assignments (one for each word), where each topic assignment
%is drawn from a distribution over topics \citep{Blei2003}.

%Supervised latent Dirichlet allocation (sLDA) builds on LDA by incorporating
%supervision in the form of an observed exponential family response 
%variable per document. As a result, sLDA
%infers topics such that the model predicts the response variable while
%improing word likelihood.  This approach has been shown to outperform both LASSO
%(L1 regularized least squares regression) and LDA followed by least
%squares regression \citep{BleiMcAuliffe2008}.

Other models that incorporate both and some form of supervision include
LabeledLDA\citep{Ramage2009}, DiscLDA\citep{DiscLDA}, models applied to 
computer vision and document networks\citep{wangbleifeifei08,RelationalLDA}.

%One set of models that are particularly relevant to HSLDA are Chang
%and Blei's hierarchical models for document networks (Relational Topic
%Models). In that family of models, they encountered a similar scenario
%where the lack of a link did not truly indicate absence. In hierarchically
%labeled data, negative labels are uncommon and the lack of a label
%in the hierarchy is not equivalent to a negative label. Therefore,
%as in the work of Chang and Blei, we employ regularization to account
%for the lack of negative labels. This will be discussed further in
\ref{sec:model}.

% Noemie: check out what I wrote here, because I am not really sure this is
% correct. 
%There have been several models that incorporate both latent models of text and
%some form of
%supervision~\citep{Ramage2009,DiscLDA,wangbleifeifei08,RelationalLDA}. One set 
%of models that are particularly relevant to HSLDA are Chang and Blei's
%hierarchical models for document networks (Relational Topic Models). In that
%family of models, they encountered a similar scenario where an unselected label 
%does not always indicate absence. In hierarchical labels, this phenomenon is
%even more pervasive -- there are no explicit negative labels, but it is also
%unclear how to treat the parents of selected labels. Like in the work of Chang
%and Blei, we employ regularization to account for the lack of negative
%labeling. In our experiments, we look at the impact of assigning positive and
%negative instances to the ancestors of selected labels.
